Enzo: An Adaptive Mesh Refinement Code for Astrophysics

### 2013-05-29 numerical-radiation-homogeneous.tex
Minor edits to radiation sections.

\enzo\ supports the use of a set of spatially uniform (but possibly
time-varying) radiation fields that can interface with the chemistry
and cooling/heating routines described elsewhere.  Many of these use
fits to the H, He and He$^+$ ionizing and photo-ionization heating
rates that are of the form

@@

where the constant coefficients $\alpha$, $\beta$, $\gamma$, $z_0$ and
$z_1$ are fits from the literature.  For radiation field types 1-3
(numbered as they appear in the \enzo\ source code and simulation
parameter values), we
give the coefficients for the photoionization (and photo-heating)
rates of H, He, and He$^+$ in Table~\ref{table:homo_coefs}.  Radiation
background types 1
and 2 are based on \citet{1996ApJ...461...20H} with two different
intrinsic quasar spectra slopes, while Type 3 is from
\citet{2012ApJ...746..125H}, modified to match the normalized field
found in \citet{Kirkman05}.

@@

Homogeneous radiation field types 5 and 6 start with a spectral shape
that is then integrated against the appropriate H, He, and He$^+$
cross-sections to compute the ionization and photo-ioniziation heating
rates (we use 400 bins logarithmically spaced from 0.74 eV to $7.24
\times 10^9$ eV).  In particular, Type 5 has a hard, featureless
quasar-like power law spectrum $f_{\nu} = f_{\rm HI} \nu^{\alpha_0}$,
where $\alpha_0 = 1.5$ by default and the spectrum is normalized at
the HI ionization edge.  Type 6 has the same spectrum, but attenuated
by a column density of $10^{22}$ cm$^{-3}$ neutral hydrogen.

>>>>

\enzo\ supports the use of a set of spatially uniform (but possibly
time-varying) radiation fields that can interface with the chemistry
and cooling/heating routines described elsewhere.  Many of these use
fits to the H, He and \Hep ionizing and photo-ionization heating
rates that are of the form

@@

where the constant coefficients $\alpha$, $\beta$, $\gamma$, $z_0$ and
$z_1$ are fits from the literature.  For radiation field types 1-3
(numbered as they appear in the \enzo\ source code and simulation
parameter values), we
give the coefficients for the photoionization (and photo-heating)
rates of H, He, and \Hep in Table~\ref{table:homo_coefs}.  Radiation
background types 1
and 2 are based on \citet{1996ApJ...461...20H} with two different
intrinsic quasar spectra slopes, while Type 3 is from
\citet{2012ApJ...746..125H}, modified to match the normalized field
found in \citet{Kirkman05}.

@@

Homogeneous radiation field types 5 and 6 start with a spectral shape
that is then integrated against the appropriate H, He, and \Hep,
cross-sections to compute the ionization and photo-ioniziation heating
rates (we use 400 bins logarithmically spaced from 0.74 eV to $7.24
\times 10^9$ eV).  In particular, Type 5 has a hard, featureless
quasar-like power law spectrum $f_{\nu} = f_{\rm HI} \nu^{\alpha_0}$,
where $\alpha_0 = 1.5$ by default and the spectrum is normalized at
the HI ionization edge.  Type 6 has the same spectrum, but attenuated
by a column density of $10^{22}$ cm$^{-3}$ neutral hydrogen.
